---
title: "R Notebook"
output: html_notebook
---
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.


```{r setup}
library('tidyverse')
# library(parallel)
setwd("C:/users/aharr/Downloads/D3_Ohlab/dec")
infiles <- dir(pattern='\\.unlimiteddepth$')
dir<-getwd()
anno<-read_tsv("covid.txt")
# I don't know what the \\. is doing in this regex. Double escaping for the 
# literal dot in the query? It works though. I reuse later.

```
Plain text in between is fine

**but markdown format text is too**

##make variable with directory and use paste0 to define where to save stuff


```{r importing_a_water}
setwd("C:/users/aharr/Downloads/D3_Ohlab/dec")

infiles <- dir(pattern='\\.unlimiteddepth$')

plottin_linear <- function(file){

## Section for getting inputs

  sample<-read_tsv(file,col_names = FALSE) %>% 
  rename(genome=X1,pos=X2,depth=X3)

covfile<-sub("\\.unlimiteddepth$",".cov", file)
cov<-read_tsv(covfile,col_names=T) %>%
   rename(genome='#rname')
cov1<-dplyr::select(cov,genome,endpos,numreads) #%>%
combinedfile<-left_join(anno,cov1,by='genome')

baicStats<-sample %>%
  group_by(genome) %>%
  summarize(mean=mean(depth), median=median(depth))

depthOf1<-filter(sample,depth >0) %>%
  group_by(genome) %>%
  summarize(Coveredby1=n())

depthOf10<-filter(sample,depth>9) %>%
  group_by(genome) %>%
  summarize(Coveredby10=n())

depthOf50<-filter(sample,depth>49) %>%
  group_by(genome) %>%
  summarize(Coveredby50=n())

depthOf100<-filter(sample,depth>99) %>%
  group_by(genome) %>%
  summarize(Coveredby100=n())

moreStats<-left_join(combinedfile,baicStats, by='genome') %>% 
  left_join(depthOf1, by='genome') %>%
  left_join(depthOf10, by='genome') %>%
  left_join(depthOf50, by='genome') %>%
  left_join(depthOf100, by='genome')
moreStats[is.na(moreStats)] <- 0 # clever

moreStats<-moreStats %>% mutate(coverage1x=Coveredby1/endpos) %>%
  mutate(coverage10x=Coveredby10/endpos) %>%
  mutate(coverage50x=Coveredby50/endpos) %>%
  mutate(coverage100x=Coveredby100/endpos) %>% 
  rename(length=endpos)


tab_oot<-sub("\\.unlimiteddepth$","_stats.txt", file)
write_tsv(moreStats,tab_oot)
# 
# ## Section for the coverage plots
sars<-filter(sample,genome=='NC_045512.2')
plot_me<-ggplot(sars, aes(x = pos, y = depth, color = file)) +
  geom_line() +
  scale_y_continuous(trans='sqrt')

png_oot<-sub("\\.unlimiteddepth$",".png", file)
ggsave(png_oot, plot = plot_me)
plot_me

  # NOTES: the rename function breaks on any empty depth file.
  # Move all empty depth files somewhere else before running this.
}

```


```{r run_that_fcn}
setwd("C:/users/aharr/Downloads/D3_Ohlab/dec")

lapply(infiles, plottin_linear)

```


anno<-read_tsv(file="covid.txt")
  sample<-read_tsv(file="D3N06_S6.unlimiteddepth",col_names = FALSE) %>% 
  rename(genome=X1,pos=X2,depth=X3)

cov<-read_tsv(file="D3N06_S6.cov",col_names=T) %>%
   rename(genome='#rname')
   cov
cov1<-dplyr::select(cov,genome,endpos,numreads) %>%
combinedfile<-left_join(anno,cov1,by='genome')

setwd("C:/users/aharr/Downloads/D3_Ohlab/flud3")
anno<-read_tsv(file="genomeflu.txt")
cov<-read_tsv(file="paragon-flu-primers.tab",col_names=T)
combinedfile<-left_join(anno,cov,by='genome')
write_tsv(combinedfile,file="stuff.txt")

setwd("C:/users/aharr/Downloads/D3_Ohlab")
sample_descs<-read_tsv("allparastatsagain.txt",col_names=T)
sam<-read_tsv("2021_d4para_desc.txt",col_names=T)
combinedfile<-inner_join(sam,sample_descs,sample=sample)
write_csv(combinedfile,file="D4para_statsagain.csv")